The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population

### 2016-12-21 repeater-vladata.tex
coauthor update
working through maura comments. updated table 1.

%\author{S.~M.~Ransom}
%\affiliation{National Radio Astronomy Observatory, Charlottesville, VA 22903, USA}

@@

\begin{abstract}
The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient. The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population. We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes. We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved temporal structure. We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
\end{abstract}

@@

This paper is part of a series that presents the first localization and unambiguous identification of an FRB host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec. Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 \citep{OPT, EVN}.

@@

We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population. Although we now know that FRBs are luminous, it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}. The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission. FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.

@@

The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb\ with the VLA. The observing strategy was to ensure simultaneous observing between the VLA and Arecibo observatories and add other observatories added on a best-effort basis. We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in figure \ref{fig:multi}. Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.

\subsection{VLA}
The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo. We concluded with a new, 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration. In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which includes all nine burst detections.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep[as in]{2015ApJ...807...16L}. To maximize sensitivity, the channel frequency width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in 8 spectral windows with 32 channels each.

Observations in August and Septmeber were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current, prototype runs on existing, CPU-based hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster. The transient search pipeline software is called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python (detail in \citet{2015ApJ...807...16L}). Images were formed for each integration at DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$. Gain calibration is read from the "telcal" system, which uses phase-only calibration on the previous gain calibrator. A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.

Burst detections and localizations were made within hours of data being recorded. The transient search starts when data are recorded, but this prototype of \rf\ is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time". Each image with a pixel higher than 6.4$\sigma$\ is saved in a summary form as a check of data quality. For each image with a pixel higher than 7.4$\sigma$, \rf\ generates a more detailed candidate visualization with an image and spectrum. More detailed analysis, including improved calibration and localization, is conducted offline.

@@

{\color{red}Jason/Shami: ok if copied from the first paper?}
During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin. The PUPPI pulsar backend was used to record total intensity spectra with time and frequency resolutions of 10.24~$\mu$s and 1.5625~MHz, respectively, and full Stokes polarization information. Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing. PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim 620$\ MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.

In total, twelve Arecibo observations had some simultaneous coverage with the VLA. Four of those observations were simultaneous with bursts detected with the VLA and one of those observations detected the same VLA burst. During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI system failed so data were recorded with {\color{red} xx (Jason?)} at C band. No detection was made in that Arecibo data. Overall, there were many more bursts detected at Arecibo than with the VLA and a more detailed analysis of those bursts will be presented in a future paper.

@@

{\color{red} copied from Laura's paper}
Observations were conducted at an observing frequency of 4.6 to 5.1~GHz. The S60mm receiver has a system equivalent flux density of 18 Jy and a full-width half-max (FWHM) beam size of 2.4\arcmin at 4.85~GHz. Pulsar search mode data were recorded with the PFFTS backend. Total intensity spectra were recorded with a time resolution of 65.5~$\mu$s and a bandwidth of 500~MHz divided into 128 frequency channels. Note, the inter-channel DM smearing time for 560~pc cm$^{-3}$\ is $\sim$0.2 msec at 4.6 GHz.

@@

We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al. 2008) for 3 hours each on four epochs starting at MJDs 57643.3351, 57645.3317, 57648.3352, and 57649.3353. Observations were made with the new digital correlator having 4096 channels across a 5 GHz bandwidth between 13--18 GHz with a 1s dump time. The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes. The AMI-LA data were binned to eight 0.625 GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}. Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.

We inspected the calibrated visibilities, and did not find any signal above 20 mJy in the 1s samples at and in the vicinity of the detected bursts. Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location. Although the statistical 3sigma upper limit is 60 uJy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30 arcsec), and the actual upper limit is larger. We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim$100 uJy. Hence, we place an upper limit of 100$\pm$10 uJy on any quiescent or possible radio "afterglow" (on $\sim$days timescale) signal from the FRB. This limit is close to the flux density measured by the VLA \citep{LOC}.

@@

This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts cover more than an octave of frequency. However, this is one of three VLA bursts with coverage by Arecibo, so the other nondetections imply that those bursts had a smaller spectral width. In fact, as described in \S \ref{sec:spec}, many of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.

@@

\begin{figure*}[htb]
\begin{center}
 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.18\columnwidth]{sgram_57623.png}
  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan7.png}
  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan13.png}
  \includegraphics[width=0.18\columnwidth]{sgram_57638.png}
  \includegraphics[width=0.18\columnwidth]{sgram_57643.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.18\columnwidth]{sgram_57645.png}
  \includegraphics[width=0.18\columnwidth]{sgram_57646.png}
  \includegraphics[width=0.18\columnwidth]{sgram_57648.png}
  \includegraphics[width=0.18\columnwidth]{sgram_57649.png}
 \end{minipage}

 \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts. Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, (bottom left) 57645, 57646, 57648, and 57649. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
 \label{fig:sgram}}
\end{center}
\end{figure*}

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc}\ \rm{cm}^{-3}$). Table \ref{tab:spec} shows the improved burst parameters using this new scheme.

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{lccccccc}
\hline
Date                & S$_{\rm{int}}$  & Image SNR & L$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$  & Center & FWHM \\
(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (Jy) & (GHz)  & (MHz) \\ \hline
57623               & 258             & 38        & 15   & 561 & 0.41                                    & 2.8 & 300 \\
57633.68            & 2000            & 179       & 120  & 554 & 1.90                                    & 3.2 & 520 \\
57633.70\tablenotemark{a} & 105       & 15        & 6    & 559 & $>$0.188                                & $<$2.5 & $>$350 \\
57638               & 65              & 12        & 4    & 556 & 0.07                                    & 3.1 & 410 \\
57643               & 375             & 100       & 21   & 560 & 0.39                                    & 2.8 & 520 \\
57645               & 38              & 13        & 2    & 572 & 0.06                                    & 2.8 & 210 \\
57646\tablenotemark{a} & 69           & 20        & 4    & 555 & $>$0.16                                 & $<$2.5 & $>$400 \\
57648\tablenotemark{b} & 97           & 25        & 6    & 559 & 0.11                                    & 2.9 & 420 \\
57649               & 110             & 36        & 6    & 552 & 0.07                                    & 2.9 & 880 \\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

Figure \ref{fig:spec} shows the spectrum of the integration and DM that maximizes the burst detection significance. After DM optimization, all bursts appear unresolved at the 5~ms time resolution of the VLA data. One possible exception is the brightest burst at 57633.68, for which roughly 10\% of the peak flux density is seen in adjacent 5~ms integrations.

\begin{figure*}[ht]
\begin{center}
 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.3\columnwidth]{spec_57623.png}
  \includegraphics[width=0.3\columnwidth]{spec_57633_scan7.png}
  \includegraphics[width=0.3\columnwidth]{spec_57633_scan13.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.3\columnwidth]{spec_57638.png}
  \includegraphics[width=0.3\columnwidth]{spec_57643.png}
  \includegraphics[width=0.3\columnwidth]{spec_57645.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.3\columnwidth]{spec_57646.png}
  \includegraphics[width=0.3\columnwidth]{spec_57648.png}
  \includegraphics[width=0.3\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz. Orthongonal circular polarizations (RR and LL) are plotted separately and example errorbars are shown at the top right of each panel. A binned spectrum is overplotted with a solid line.
\label{fig:spec}}
\end{center}
\end{figure*}

The burst spectra are generally characterized by a broad, Gaussian shape that with strong inter-channel modulation. We fit a Gaussian shape to each burst to estimate their characteristic width and peak flux, as summarized in Table \ref{tab:spec}. The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution. This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
% TODO: fit with generative model with 100% amplitude modulations (emcee?)

@@

\subsubsection{Circular Polarization}
The VLA S-band recievers natively measure circular polarization, although for observing efficiency we chose not include polarization calibration procedures. Crude constraints on circular polarization are possible by comparing the burst intensity in right and left-hand polarized data products. The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%. \frb\ was located 2.3 arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo). Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{luminosity_disn}
\caption{Probability distribution of powerlaw luminosity model for the nine VLA bursts from \frb. The powerlaw is referenced to $L=2\times10^{38}$\ erg.
\label{fig:lumd}}
\end{center}
\end{figure}

>>>>

\author{S.~M.~Ransom}
\affiliation{National Radio Astronomy Observatory, Charlottesville, VA 22903, USA}

@@

\begin{abstract}
The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient. The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population. We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes. We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved intrinsic temporal structure. We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
\end{abstract}

@@

This paper is part of a series that presents the first localization and unambiguous identification of an FRB host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec. Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 \citep{OPT, EVN}.

@@

We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are luminous, but it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}. The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission. FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.

@@

The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb\ with the VLA. The observing strategy was to ensure simultaneous observing between the VLA and Arecibo observatories and add other observatories on a best-effort basis. We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:multi}. Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.

\subsection{VLA}
The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo. We concluded with a new, 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration. In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which include all nine burst detections.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep[as in]{2015ApJ...807...16L}. To maximize sensitivity, the channel frequency width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each.

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on existing, CPU-based hardware of the VLA correlator backend with transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}. Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 554--560 pc cm$^{-3}$. Gain calibration is read from the ''telcal'' system, which uses phase-only calibration on the previous gain calibrator. A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.

Burst detections and localizations were made within hours of data being recorded. The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ''quasi real-time''. For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image. Summary statistics are saved for images with S/N higher than 6.4, which captures the tail of the thermal noise distribution without adding significant computational or data volume burden. Each image with a pixel with S/N higher than 7.4 is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed candidate visualization with an image and spectrum. More detailed analysis, including improved calibration and localization, is conducted offline.

@@

During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend. The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz. We recorded total full Stokes polarization intensity spectra with time at a resolution of 10.24~$\mu$s. Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing. The ull width at half maximum (FWHM) beam size at band center is 3.3\arcmin.

In total, twelve Arecibo observations had some simultaneous coverage with the VLA. Four of those observations were simultaneous with bursts detected with the VLA and one of those observations detected the same VLA burst. During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI system failed so data were recorded with {\color{red} xx (Jason?)} at C band. No detection was made in those Arecibo data. Overall, there were many more bursts detected at Arecibo than with the VLA and a more detailed analysis of those bursts will be presented in a future paper.

@@

Effelsberg observations were conducted with the S60mm receiver at an observing frequency of 4.6 to 5.1~GHz. Total intensity spectra were recorded by the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s and 128 frequency channels. The system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin at 4.85~GHz.

@@

We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al. 2008) for 3 hours each on four epochs starting at MJDs 57643, 57645, 57648, and 57649. Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time. The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes. The AMI-LA data were binned to eight 0.625~GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}. Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.

We inspected the calibrated visibilities, and did not find any signal above 20 mJy in the 1s samples at and in the vicinity of the detected bursts. Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location. Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger. We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy. Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio ''afterglow'' (on $\sim$days timescale) signal from the FRB. This limit is close to the flux density measured by the VLA \citep{LOC}.

@@

This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts emit over more than an octave of frequency. However, this is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width. However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely. However, as described in \S \ref{sec:spec}, some of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.

@@

\begin{figure*}[htb]
\begin{center}
% \begin{minipage}{2\columnwidth}
%  \includegraphics[width=0.18\columnwidth]{sgram_57623.png}
%  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan7.png}
%  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan13.png}
%  \includegraphics[width=0.18\columnwidth]{sgram_57638.png}
%  \includegraphics[width=0.18\columnwidth]{sgram_57643.png}
% \end{minipage}
%
% \begin{minipage}{2\columnwidth}
%  \includegraphics[width=0.18\columnwidth]{sgram_57645.png}
%  \includegraphics[width=0.18\columnwidth]{sgram_57646.png}
%  \includegraphics[width=0.18\columnwidth]{sgram_57648.png}
%  \includegraphics[width=0.18\columnwidth]{sgram_57649.png}
% \end{minipage}
%
% \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts. Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, (bottom left) 57645, 57646, 57648, and 57649. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
 \includegraphics[width=0.9\columnwidth]{sgram_57623.png}
 \caption{**Placeholder** Fill in with AO+VLA dynamic spectrum.
 \label{fig:sgram}}
\end{center}
\end{figure*}

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). Table \ref{tab:spec} shows the improved burst parameters using this new scheme.

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{lccccccc}
\hline
Date                & S$_{\rm{int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$  & Center & FWHM \\
(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (Jy) & (GHz)  & (MHz) \\ \hline
57623               & 258             & 38        & 7.1  & 561 & 0.41                                    & 2.8 & 300 \\
57633.68            & 2000            & 179       & 56   & 554 & 1.89                                    & 3.1 & 520 \\
57633.70\tablenotemark{a} & 105       & 15        & 5.5  & 559 & $>$0.28                                & $<$2.5 & $>$350 \\
57638               & 65              & 12        & 1.7  & 556 & 0.07                                    & 3.1 & 430 \\
57643               & 375             & 100       & 11   & 560 & 0.39                                    & 2.8 & 530 \\
57645               & 38              & 13        & 1.0  & 572 & 0.05                                    & 2.8 & 350 \\
57646\tablenotemark{a} & 69           & 20        & 3.4  & 555 & $>$0.16                                 & $<$2.5 & $>$380 \\
57648\tablenotemark{b} & 97           & 25        & 2.6  & 559 & 0.11                                    & 2.8 & 420 \\
57649               & 110             & 36        & 3.7  & 552 & 0.07                                    & 2.9 & 870 \\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

Figure \ref{fig:spec} shows the spectrum of the integration and DM that maximizes the burst detection significance. After DM optimization, most bursts appear unresolved at the 5~ms time resolution of the VLA data. One exception is the brightest burst at 57633.68, for which roughly 10\% of the peak flux density is seen in adjacent 5~ms integrations. **elaborate on 57633.68 time width**

\begin{figure*}[ht]
\begin{center}
 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.4\columnwidth]{spec_57623.png}
  \includegraphics[width=0.4\columnwidth]{spec_57633_scan7.png}
  \includegraphics[width=0.4\columnwidth]{spec_57633_scan13.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.4\columnwidth]{spec_57638.png}
  \includegraphics[width=0.4\columnwidth]{spec_57643.png}
  \includegraphics[width=0.4\columnwidth]{spec_57645.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.4\columnwidth]{spec_57646.png}
  \includegraphics[width=0.4\columnwidth]{spec_57648.png}
  \includegraphics[width=0.4\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz. Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
The solid line is a best-fit Gaussian model derived from spectra binned by a factor of 4.
\label{fig:spec}}
\end{center}
\end{figure*}

The burst spectra are generally characterized by a broad, Gaussian shape with strong inter-channel modulation. We fit a Gaussian shape to each burst to estimate its characteristic width and peak flux (Table \ref{tab:spec}). The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution. This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
% TODO: fit with generative model with 100% amplitude modulations (emcee?)

@@

\subsubsection{Circular Polarization}
The VLA S-band recievers natively measure circular polarization, although for observing efficiency we chose not include polarization calibration procedures. Crude constraints on circular polarization are possible by comparing the burst intensity in right and left-hand polarized data products. The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%. \frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo). Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{luminosity_cdisn}

\includegraphics[width=0.9\columnwidth]{luminosity_disn}
\caption{\emph{Top:} Cumulative luminosity distribution with powerlaw fit for the nine VLA bursts from \frb. \emph{Bottom:} Probability distribution of luminosity model of the differential luminisotiy distribution. The powerlaw is referenced to $L=2\times10^{38}$\ erg.
\label{fig:lumd}}
\end{center}
\end{figure}
